Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
matt's grant number, revised to-do lists
body text and tables for first half of fa expts

TO DO: INTRODUCE THIS SECTION

@@

  \begin{table}
    % \centering
    \caption{$dl,lh$ decompositions are
      more correlated with the fluency-adequacy average than BLEU$_4$
      or $dlh$ decompositions.}
    \begin{tabular}{lr}
      metric  &    $r$ \\
      \hline
      $F[dl,lh]$ &   0.226 \\
       % # +1 smoothing
      BLEU$_4$ &   0.218 \\
      $F[dlh]$ &     0.185 \\
      TER &      -0.173 \\
    \end{tabular}
    \label{tab:facorr:subgraphs}
\end{table}

Table~\ref{tab:facorr:subgraphs} indicates that: using
partial-labeling (dl,lh) much better than full link. Also, using
Charniak parser as labeler seems to work, LFG not necessary
Here, $n=1$ and only the $F[\cdot]$ score combination is shown.

@@

\item EXPT 
  combining precision, recall naively vs. combining items

\begin{verbatim}
  F(1g,2g,dl,lh)        0.237
  prmeans(1g,2g,dl,lh)  0.217

  F(dl,lh)              0.226
  prmeans(dl,lh)        0.208
\end{verbatim}

  point: combining individual items naively (before computing
  precision and recall) seems better than naively combining precisions
  and recalls (too many chances for zeroes?)

@@

>>>>

To explore members of the DPM metric family, we explore the
correlations of various configurations against a corpus of human
judgments of fluency and adequacy.

% TO DO: more to say here?

@@

\subsection{Exploring decompositions}
We begin by comparing some of the simplest DPM measures to baseline
measures case-sensitive BLEU (4-grams, with add-one smoothing) and
TER.  For these first experiments, we consider only the 1-best parse
($n=1$).
\begin{table}
  \caption{Comparing $dl,lh$ to $dlh$ and baselines.}
  \label{tab:facorr:subgraphs}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[dl,lh]$ &   0.226 \\
    % # +1 smoothing
    BLEU$_4$ &   0.218 \\
    $F[dlh]$ &     0.185 \\
    TER &      -0.173 \\
    \hline
  \end{tabular*}
\end{table}
In table~\ref{tab:facorr:subgraphs} we see that using the
partial-label $dl,lh$ decomposition has a better correlation with the
fluency/adequacy scores than TER or BLEU$_4$.  These results confirm,
with a PCFG, what \inlinecite{owczarzak07labelleddepseval} found with
an LFG parser: that partial-dependency matches are better correlated
with human judgments than full-dependency links.

In table~\ref{tab:facorr:combinations}, we compare among several other
members of the DPM family. 
\begin{table}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
%
    $F[dl,lh]$            &  0.226 \\
    $\mu_{PR}[dl,lh]$      &  0.208 \\
    \hline
  \end{tabular*}
  \caption{Comparing combination methods $F[\cdot]$ and
    $\mu_{PR}[\cdot]$, and comparing the $1g,2g,dl,lh$ decomposition
    with the $dl,lh$ decomposition.}
  \label{tab:facorr:combinations}
\end{table}
Here, we find that combining the decompositions naively in $F[\cdot]$
(before computing precision and recall) has a better $r$ than the
harmonic mean of precision and recall subscores in $\mu_{PR}[\cdot]$.
We also see that including some simple surface-matching features (the
$1g,2g$ n-gram decompositions) improves correlations further beyond
the simple $dl,lh$ features.

% (too many chances for zeroes?)

\subsection{Exploring parse expectations}

@@

@@

Matthew Snover is supported under the GALE Program, DARPA/IPTO
Contract No. HR0011-06-C-0022.
